### 2012-02-13 paper.tex
Updated various parts of the manuscript

\noindent \normalsize{In the current paper high-quality mass spectrometry data of the oscillatory behaviour of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure is presented. The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio. The frequency of the oscillations tends to increase in with time while the duty cycle remains constant. Jeg synes, at vi skal skrive abstractet om. Det skal i alle være længere og mere præcist.}
%Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

@@

Here we report oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure. Oscillating reactions on platinum at UHV-conditions has been studied extensively and is know to originate from surface reconstructions during the oscillations\cite{Ertl2008}. It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures shows oscillatory behavior on single crystals of Pt, Pd and Ir. Recent studies have proposed a mechanism on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface. CO oxidation oscillations has also been observed on Pt thin-films\cite{Lund2000} and in macroscopic flow reactors\cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.

@@

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At O$_2$:CO ratio of $\sim0.08$ and a geometrical platinum coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp. After the initial lightoff the sample is cooled to room temperature. When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
  \label{fgr:initial_treatment}
\end{figure}
The qualitative same behavior has been reproduced on a large number of samples where oscillations also occur. Generally the oscillations have been seen on samples from 3\,nm to 9\,nm and in a wide coverage regime. A geometrical coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.

The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour. An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\% conversion. Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached. Shortly after reaching 50\% conversion the sample again ignites and convert all CO to CO$_2$. After a short full conversion period the sample again deactivates and the cycle repeats itself. The ratio between periods of high and low conversion are very different among samples, but for a given sample the ratio normally does not change even though the oscillation period consistently becomes longer as the experiment progresses.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself. This extremely long oscillation period is not commonly seen and was a result of carefull parameter tuning. Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,minutes.}
  \label{fgr:full_oscillation}
\end{figure*}

@@

After the initial lightoff experiment the nanoparticles show stable self-sustained oscillation. After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}. Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time. Hereafter the oscillations are more irregular as shown in Figure~\ref{fgr:long_measurement}. At experiment end the oscillation period is between 45 and 20 minutes.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from a four day measurement. Here data from shortly after the initial treatment, after 2800\,min. of oscillation time and after 5900\,min. are shown. After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}. Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from the 4 day long experiment. The oscillation period become more irregular with time while the on/off ratio remains constant. Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
  \label{fgr:extracts}
\end{figure}

The oscillation period becomes more irregular with progressing experiment time although the on/off ratio remains constant during the entire experiment time. Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure~\ref{fgr:full_oscillation}. A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered. At approximately 50\,\% conversion lightoff occurs and the sample is in full conversion.

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s}
  \label{fgr:temperature_dependence}
\end{figure}
A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}. By changing the temperature 5$^\circ$C the oscillation period is changed by more than a factor of 10.

\section{Discussion}
This mechanism is, however, not relevant at atmospheric pressures and thus another physical mechanism must be governing the oscillations at high pressures.

@@

Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.  It is hence concluded that the oscillations is a feature related to the catalyst. It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theory \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface. A detailed proposal for the reaction mechanism on Pd has been developed \cite{Hendriksen2010} and our data is consistent with this model. According to the proposed model, the bare metal surface is less active than the oxidized surface. It is further suggested that a high concentration of steps will thermodynamically favor the reduced surface and a low concentration of steps will favor the oxidized surface. The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness. Thus the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and thus lower the rate. After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate. In this study, we measure on Pt nanoparticles which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time, the reaction itself will smoothen the particles, further pushing towards an oxidation of the particles. Gradually as the particles towards the outlet oxidizes the turn-over will increase and the general CO concentration will decrease, further promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO. At a given point the CO concentration will become low enough that a light-off like phenomenon will set in and the sample will show full conversion. If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration. The increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles. Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the de-activation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.

@@

%This is in good agreement with \cite{Hendriksen2010} where a strong temperature dependence was predicted but not actually demonstrated.

\section{Conclusion}
We have for the first time demonstrated oscillating CO oxidation on Pt nanoparticles measured with high-quality mass-spectrometry. We have shown oscillations wide range of sizes of nanoparticles and a large span i CO-concentration. Burde vi ikke skrive lidt mere om, hvad vi egentlig præsenter? Vi viser egentlig ikke så meget med størrelseafhængighed og CO-koncentrations-eksperimenter.

>>>>

\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behaviour of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure is presented. The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio. The frequency of the oscillations is very well defined and show clear tendency to increase in with time. A plausible mechanism for the oscillations is proposed based on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

@@

Here we report oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure. Oscillating reactions on platinum at UHV-conditions has been studied extensively and is know to originate from surface reconstructions during the oscillations\cite{Ertl2008}. This mechanism is, however, not relevant at atmospheric pressures and thus another physical mechanism must be governing the oscillations at high pressures. It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures shows oscillatory behavior on single crystals of Pt, Pd and Ir. Recent studies have proposed a mechanism on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface. CO oxidation oscillations has also been observed on Pt thin-films\cite{Lund2000} and in macroscopic flow reactors\cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.

@@

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At O$_2$:CO ratio of $\sim0.08$ and a geometrical platinum coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp. After the initial lightoff the sample is cooled to room temperature. When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
  \label{fgr:initial_treatment}
\end{figure}
The qualitative same behavior has been reproduced on a large number of samples, many of them showing oscillations. We have tried with particles with sized between 3\,nm and 9\,nm, but no clear size dependence was seen, most of the experiments presented here was done with 3\,nm particles. A geometrical coverage of 0.1\% gave the most consistent oscillations. Higher coverages also showed oscillations, but often only on the inital heating and cooling ramps, but only very rarely did they show prolonged oscillations at constant temperature.

The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour. Once a sample start to oscillate consistently, it will keep performing self-sustained oscillations for as long as the experiemnt is allowed to run. We have not seen a single sample stop oscillating once the self-sustained oscillations had started. An example of a very slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\% conversion. Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached. Shortly after reaching 50\% conversion the sample again ignites and convert all CO to CO$_2$. After a short full conversion period the sample again deactivates and the cycle repeats itself. The ratio between periods of high and low conversion are very different among samples, but for a given sample the ratio normally does not change even though the oscillation period consistently becomes longer as the experiment progresses.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself. This extremely long oscillation period is not commonly seen and was a result of carefull parameter tuning. Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,minutes.}
  \label{fgr:full_oscillation}
\end{figure*}

@@

After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}. Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time. Hereafter the oscillations are more irregular as shown in Figure~\ref{fgr:long_measurement}. At experiment end the oscillation period is between 45 and 20 minutes.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four day measurement. Here data from shortly after the initial treatment, after 2800\,min. of oscillation time and after 5900\,min. are shown. After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}. Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from the 4 day long experiment. The oscillation period become more irregular with time while the on/off ratio remains constant. Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
  \label{fgr:extracts}
\end{figure}

The oscillation period becomes more irregular with progressing experiment time although the on/off ratio remains constant during the entire experiment time. Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure~\ref{fgr:full_oscillation}. A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered. At approximately 50\% conversion lightoff occurs and the sample is in full conversion.

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s}
  \label{fgr:temperature_dependence}
\end{figure}
A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}. By changing the temperature 5$^\circ$C the oscillation period is changed by more than a factor of 10. The magnitude of the change is not completely consistent across all measured samples, but all samples do show a very large temperature dependency, in some cases a change of a few degrees will consistently turn on and off the oscillations.

@@

\section{Discussion}
Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds. It is hence concluded that the oscillations is a feature related to the catalyst. It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theory \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface. A detailed proposal for the reaction mechanism on Pd has been developed by Hendriksen \textit{et. al.}\cite{Hendriksen2010} and our data is consistent with this model.

According to the proposed model, the bare metal surface is less active than the oxidized surface. It is further suggested that a high concentration of steps will thermodynamically favor the reduced surface and a low concentration of steps will favor the oxidized surface. The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness. Thus the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and thus lower the rate. After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.

In this study, we measure on Pt nanoparticles which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time, the reaction itself will smoothen the particles, further pushing towards an oxidation of the particles. Gradually as the particles towards the outlet oxidizes the turn-over will increase and the general CO concentration will decrease, further promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.

Even though the temperature is kept constant, the light-off temperature will decrease as the CO-concentration increases, and at a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion. If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration. The further increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles. Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the de-activation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.

@@

An interesting feature in the data, is the very large temperature dependence. This property was actually predicted by Hendriksen et. al \cite{Hendriksen2010} when they proposed the model, and to our knowledge, this is the first time the temperature dependence is measured.

\section{Conclusion}
We have for the first time demonstrated oscillating CO oxidation on Pt nanoparticles measured with high-quality mass-spectrometry. We have found that the samples will increasing the oscillation period over time and show a dramatic temperature dependence. Oscillations has been seen on a wide range of nanoparticles from 3\,nm to 9\,nm and within a large CO-concentration window, however, it is evident that very oxygen rich conditions is needed for the oscillations to happen.
